Stochastic Gradient Descent

### 2018-05-11 sgd/sgd.tex
o

	OLS has a closed form solution: $\hat{\bm{\beta}} =
	(\bm{X}'\bm{X})\bm{X}'\bm{Y}$ \\~\\

@@

	Some familiar tools for finding $\hat{\mathbf{w}}$ no longer work well
	\\~\\

@@

\begin{frame}
	\frametitle{Gradient descent is an iterative search procedure}
	\begin{figure}[h]
	\centering
	\includegraphics[scale=0.33]{Sketch}
	\end{figure}
\end{frame}

@@

	Stop if gradient $\leq \epsilon$ \\~\\

@@

	$$
	{\mathbf{w}^{(t+1)}} = \mathbf{w}^{(t)} - \gamma \nabla_w
	L(f(\bm{w}^{(w)}; \mathbf{X}_{\textcolor{red}{i}}), Y_{\textcolor{red}{i})}
	$$ \\~\\

@@

\begin{frame}
	\frametitle{SGD is very popular in academia and industry}
	Many, many, \textit{many} statistical learning models use SGD to fit weights \\~\\

	If a Silicon Valley press release uses any of the following phrases...
	\begin{itemize}
		\item \small ``Neural networks''
		\item ``Machine learning''
		\item ``AI'' 
	\end{itemize}

>>>>

	OLS has a closed form solution: $\hat{\bm{\beta}} =
	(\bm{X}'\bm{X})^{-1}\bm{X}'\bm{Y}$ \\~\\

@@

	Some familiar tools for finding $\hat{\mathbf{w}}$ may no longer work well
	\\~\\

@@

\begin{frame}
	\frametitle{Gradient descent visualized}
	\begin{figure}[h]
	\centering
	\includegraphics[scale=0.33]{Sketch}
	\end{figure}
\end{frame}

@@

	Stop if $||\mathrm{gradient}||_2$ $\leq \epsilon$ \\~\\

@@

	$$
	{\mathbf{w}^{(t+1)}} = \mathbf{w}^{(t)} - \gamma \nabla_w
	L(f(\bm{w}^{(t)}; \mathbf{X}_{\textcolor{red}{i}}), Y_{\textcolor{red}{i})}
	$$ \\~\\

@@

\begin{frame}
	\frametitle{SGD is very popular in academia and industry}
	Many statistical learning models use SGD to fit weights \\~\\

	Particularly popular for neural networks (backpropagation) \\~\\

	If a Silicon Valley press release uses any of the following phrases...
	\begin{itemize}
		\item \small ``Machine learning''
		\item \small ``AI'' 
		\item \small ``Cognitive computing''
	\end{itemize}
